Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-14 docs/ms.tex
Update ms.tex
up date

In this section we calculate the mean square error of mean of posterior samples from the true(input) $g$.  We show the mean of posterior samples has smaller mean square error than the mean ellipticity estimator but has higher mean square error than the direct Bayesian estimates which could be made if we knew the exact intrinsic shape distribution.
In figure 5 we show how the mean square error changes with the number of galaxies and patches, and make a comparison with mean ellipticity estimator and direct Bayesian estimates. From the figure we can see that when the number of sky patches is small our hierarchical Bayesian method does not necessarily has lower mean square error than mean ellipticity estimator. However it becomes smaller and approach to the result of direct Bayesian estimate which is the best estimate we can possibly make.

>>>>

In this section we calculate the mean square error of mean of posterior samples from the true(input) $g$.  We show that the mean of posterior samples has smaller mean square error than the mean ellipticity estimator but has higher mean square error than the direct Bayesian estimates which could be made if we knew the exact intrinsic shape distribution.
In figure 5 we show how the mean square error changes with the number of galaxies and patches, and make a comparison with mean ellipticity estimator and direct Bayesian estimates. From the figure we can see that when the number of sky patches is small our hierarchical Bayesian method does not necessarily has lower mean square error than mean ellipticity estimator. However it becomes smaller and approach to the result of direct Bayesian estimate which is the best estimate we can possibly make.
